Enforced Invariant Confluence

### 2018-04-22 doc/paper/sections/abstract.tex
Formatting tweaks.

\begin{abstract}
Strongly consistent systems are easy to reason about but face fundamental
limitations in availability and performance. Weakly consistent systems can be
implemented with very high performance, but place a burden on the application
developer to reason about complex interleavings of execution.
Invariant-confluence provides a formal framework for understanding when we can
get the best of both worlds. An invariant-confluent object can be efficiently
replicated with no coordination needed to preserve its invariants.  However,
actually determining whether or not an object is invariant-confluent is
challenging (undecidable). In this paper, we establish conditions under which a
commonly used sufficient condition for invariant confluence is both necessary
and sufficient. We use this condition to design a general-purpose interactive
invariant-confluence decision procedure and a novel sufficient condition which
can be checked automatically. We then take a step beyond invariant-confluence
and introduce a generalization of invariant-confluence, called segmented
invariant-confluence, which allows us to replicate non-invariant-confluent
objects with a small and tunable amount of coordination. Implementing our
theoretical findings in a system called Lucy, we evaluate our methods on a
number of case studies and benchmarks showing that... TODO: Perform evaluation
:P.
% Strongly consistent systems are easy to reason about but are slow. Weakly consistent systems are fast but hard to reason about. Invariant-confluence gives a formal framework to reason about when data can be replicated without any coordination needed to maintain invraints, the best of borth worlds. However, determining whether an object is invariant-confluent is hard. In this paper, we establish conditions under which a commonly used sufficient condition for invariant confluence is both necessary and usfficient. We use this condition to design a general-purpose interactive decision procedure and a novel sufficient condition which can be checked automatically. We then take a step beyond invariant-confluence and introduce a generalization of invariant-confuluence, called segmented invariant-confluence which allows to replicate objects with a minimal amount of coordination that are otherwise not invariant-confluent. We implement all this in a system called lucy and look at a bunch of stuff.
\end{abstract}

>>>>

\begin{abstract}
Strongly consistent systems are easy to reason about but face fundamental
limitations in availability and performance. Weakly consistent systems can be
implemented with very high performance but place a burden on the application
developer to reason about complex interleavings of execution.
\Invariantconfluence{} provides a formal framework for understanding when we
can get the best of both worlds. An \invariantconfluent{} object can be
efficiently replicated with no coordination needed to preserve its invariants.
However, actually determining whether or not an object is \invariantconfluent{}
is challenging (undecidable). In this paper, we establish conditions under
which a commonly used sufficient condition for \invariantconfluence{} is both
necessary and sufficient and use this condition to design (a) a general-purpose
interactive \invariantconfluence{} decision procedure and (b) a novel
sufficient condition which can be checked automatically. We then take a step
beyond \invariantconfluence{} and introduce a generalization of
\invariantconfluence{} called segmented \invariantconfluence{}, which allows us
to replicate non-\invariantconfluent{} objects with a small and tunable amount
of coordination. We implemented our theoretical findings in a prototype called
Lucy and found that our decision procedures efficiently handle workloads
including foreign key constraints, rollups, escrow transactions, etc.  We also
found that segmented \invariantconfluent{} replication can deliver up to an
order of magnitude more throughput than linearizable replication for low
contention workloads and comparable throughput for medium to high contention
workloads.
\end{abstract}

### 2018-04-22 doc/paper/sections/conclusion.tex
Formatting tweaks.

\section{Conclusion}
TODO

>>>>

\section{Conclusion}
This paper revolved around two major contributions.  First, we developed a
deeper understanding of invariant-closure and \invariantconfluence{} by looking at the
two criteria with reachability in mind. We found that invariant-closure fails
to incorporate a notion of reachability, and using this intuition, we developed
conditions under which invariant-closure and \invariantconfluence{} are equivalent.
Second, we proposed a new consistency model and generalization of
\invariantconfluence{}, segmented \invariantconfluence{}, that can be used to replicate
non-invariant-confluent objects with a small amount of coordination while still
preserving their invariants. We also found that segmented \invariantconfluence{}
naturally subsumes existing techniques for maintaining invariants of replicated
objects (e.g.\ locking and escrow transactions).
